\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-11 paper/paper.Rnw
Tweaks

colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "design", "subj_id", "weights", "detected", "log_time", "RandomEf", "FixedEf", "residual")

@@

full <- mutate(full, design = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"),
               r = round(correlation, 1),
               rsgn = ifelse(r >= 0, 1, 0),
               rabs=abs(r),
               alpha = log(0.05/0.95),
               attempts = sapply(strsplit(as.character(full$response_0), ","), length), #count number of selections in response_0 column
               weights = 1/attempts)
full <- full %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#split multiple selections in response_0 into different rows
full <- mutate(full, correct = ifelse(response_0 == actual_location, 1, 0),
                   score = ifelse(correct==1, (20-attempts)/19, 0))
full <- select(full, subj_id, correct, score, r, rsgn, rabs, smoothed, n, design, log_time, response_0, actual_location, pic_id, choice_reason, attempts, weights, alpha)

@@

\iffalse
\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "design")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(design=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(design=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(design=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(design=="Scatterplot", correct, 0)))
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(x="Correlation", y="Scatterplot power minus Overlaid Lines") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. The largest differences appear in negative correlation, where the scatter plot is more powerful.}
 \label{powerdiff}
\end{figure}
\fi

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
time <- select(full, design, log_time, correct,, sign)
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, design, rsgn), m=mean(log_time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2)
@
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
    \label{time} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf <- select(full, design, conf_level, correct, sign)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, design, rsgn), m=mean(conf_level))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2)
@
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
  \label{confidence} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf2 <- select(full, conf_level, correlation, smoothed, n, design) #c(7, 15
qplot(correlation, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~design+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
 \label{confidence2}
\end{figure}

@@

\begin{enumerate}
\item $x_{1,i}$ is the absolute value of the true plot correlation, $\rho$, with $i \in \{0.3, 0.5, 0.7, 0.9\}$,
\item $x_{2,j}$ is a dummy variable for the sign of the true plot correlation, with $j = 0$ for negative correlation, 
\item $x_{3,k}$ is a dummy variable for the smoothing procedure, with $k = 0$ for unsmoothed data, 
\item $x_{4,t}$ is the sample size, with $t \in \{12, 24, 48, 96\}$ ,
\item $x_{5,l}$ denotes the plot design, with $l =0$ for the overlaid lines type,
\item $z_{s}$ is an observer specific random effect, with $s = 1, 2, \dots , 157$.
\end{enumerate}

@@

Where a subject made multiple selections from the same lineup, each selection is treated as a separate data point with a probability weighting equal to the inverse of the number of selections.

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
# data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), design=c(0,1),
#                                      subj_id=full.sub$subj_id))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE) # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), design = ifelse(design==0, "Overlaid Lines", "Scatterplot"), design = ifelse(smoothed==1, paste(design, "(Smoothed)", sep=" "), design),  diff = round(RandomEf - FixedEf,5))
randomeffects <- summarise(group_by(prediction, subj_id), re=max(diff)) #all values of diff are identical for a given subject, max chosen just as a function to select one of them
prediction <- select(prediction, r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf)
prediction <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))

qplot(r, RandomEf, data=prediction, color=design, 
      group=interaction(subj_id, design), geom="line", alpha=I(0.1)) + 
  scale_color_manual("Plot Design", values=c("#33AA33", "#9977EE", "#FF9933", "#00DDAA")) + 
  xlab("Correlation") + ylab("Estimated Power") +
  geom_line(aes(y=FixedEf), size=2, alpha=1) + theme_bw() + facet_wrap(~t, ncol = 2) + theme(aspect.ratio=1.2)
@
  \caption{Predicted power fit from the mixed effects logit power model. The thicker lines shows the fixed effects prediction while the thinner lines show the range of random effects, the observer's visual ability. The weakness of the overlaid line graph in negative correlation and the scatter plot's gain from sample size are highlighted.}
  \label{powermodel}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='powermodel', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}

@@

The structure of the model is similar to that in Equation~\ref{modelpower} except the link function is removed and a new variable, $x_{6,m}$ is introduced, with $m = \{0,1\}$ indicating if the subject detected the true plot.

\begin{table}[htp]
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines. Fitted with the MIXED procedure in SAS.}
\label{tab2}
\centering
<<timefit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
time.fit <- time.fit[c(1, 5, 6, 2, 3, 4, 7, 8, 12, 13, 9, 10, 11, 14),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "abs(r)", "sign(r)", "abs(r)*sign(r)", "detected", "design", "design*Smoothed", "design*t", "design*abs(r)", "design*sign(r)", "design*abs(r)*sign(r)", "design*detected")
time.fit$Effect <- NULL
colnames(time.fit) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(time.fit[1:14,], format="latex", digits=2)
@
\end{table}

@@

\begin{table}[htbp]
\label{tab3}
\centering
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
turk.tbl <- select(bylineup, design, smoothed, r, n, correct, evals)
turk.tbl$result <- paste(round(turk.tbl$correct, 0), turk.tbl$evals, sep="/")
turk.tbl <- turk.tbl[order(turk.tbl$r, turk.tbl$n),]
scatter.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Scatterplot")$result, ncol=8))
scatter.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Scatterplot")$result, ncol=8))
line.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Overlaid Lines")$result, ncol=8))
line.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Overlaid Lines")$result, ncol=8))
colnames(scatter.uns) <- c("", "-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(scatter.sm) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.uns) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.sm) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
kable(scatter.uns, format="latex", caption="Unsmoothed scatter plot results")
kable(scatter.sm, format="latex", caption="Smoothed scatter plot results")
kable(line.uns, format="latex", caption="Unsmoothed overlaid line results")
kable(line.sm, format="latex", caption="Smoothed overlaid line results")
@
\end{table}

Table~\ref{tab3} contains the true plot detections / attempts for each lineup in the data collection. Results ignore multiple selection weighting. True plot correlation is on the x axis and t is on the y axis.

\begin{figure}[htbp]
\centering
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\label{map}
\end{figure}

Figure~\ref{map} shows the location of the recruited subjects. The majority reside in the United States but some are spread around other countries in Europe and Asia.

>>>>

colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "design", "subj_id", "weights", "detected", "log_time", "RandomEf", "FixedEf", "residual")
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), design = ifelse(design==0, "Overlaid Lines", "Scatterplot"), design = ifelse(smoothed==1, paste(design, "(Smoothed)", sep=" "), design),  diff = round(RandomEf - FixedEf,5))

@@

full <- mutate(full, design = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"),
               r = round(correlation, 1),
               rsgn = ifelse(r >= 0, 1, 0),
               rabs=abs(r),
               alpha = log(0.05/0.95),
               attempts = sapply(strsplit(as.character(full$response_0), ","), length), #count number of selections in response_0 column
               weights = 1/attempts)
full <- full %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#split multiple selections in response_0 into different rows
full <- mutate(full, correct = ifelse(response_0 == actual_location, 1, 0),
                   score = ifelse(correct==1, (20-attempts)/19, 0))
full <- select(full, subj_id, correct, score, r, rsgn, rabs, smoothed, n, design, log_time, response_0, actual_location, pic_id, choice_reason, attempts, weights, alpha, conf_level)

@@

\iffalse
\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
#prop <- bylineup[order(bylineup$r, bylineup$n, bylineup$smoothed),c("smoothed", "n", "evals", "total", "r", #"design")]
#prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(design=="Overlaid Lines", total, 0)),
#                                                  l.correct=sum(ifelse(design=="Overlaid Lines", score, 0)),
#                                                  s.attempt=sum(ifelse(design=="Scatterplot", total, 0)),
#                                                  s.correct=sum(ifelse(design=="Scatterplot", score, 0)))
#prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
#               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
#               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
##               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
#ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
#        geom_hline(aes(yint=0, colour="red")) + labs(x="Correlation", y="Scatterplot power minus Overlaid Lines") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. The largest differences appear in negative correlation, where the scatter plot is more powerful.}
 \label{powerdiff}
\end{figure}
\fi

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
time <- select(full, design, log_time, correct, rsgn)
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, design, rsgn), m=mean(log_time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2)
@
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
    \label{time} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf <- select(full, design, conf_level, correct, rsgn)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, design, rsgn), m=mean(conf_level))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2)
@
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
  \label{confidence} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf2 <- select(full, conf_level, r, smoothed, n, design) #c(7, 15
qplot(r, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~design+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
 \label{confidence2}
\end{figure}

@@

\begin{itemize}
\item $x_{1,i}$ is the absolute value of the true plot correlation, $\rho$, with $i \in \{0.3, 0.5, 0.7, 0.9\}$,
\item $x_{2,j}$ is a dummy variable for the sign of the true plot correlation, with $j = 0$ for negative correlation, 
\item $x_{3,k}$ is a dummy variable for the smoothing procedure, with $k = 0$ for unsmoothed data, 
\item $x_{4,t}$ is the sample size, with $t \in \{12, 24, 48, 96\}$ ,
\item $x_{5,l}$ denotes the plot design, with $l =0$ for the overlaid lines type,
\item $z_{s}$ is an observer specific random effect, with $s = 1, 2, \dots , 157$.
\end{itemize}

@@

If a subject made multiple selections from the same lineup, each selection is treated as a separate data point with a probability weighting equal to the inverse of the number of selections.

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
# data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), design=c(0,1),
#                                      subj_id=full.sub$subj_id))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE) # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
#all values of diff are identical for a given subject, max chosen just as a function to select one of them
predplot <- select(prediction, r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf)
predplot <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))

qplot(r, RandomEf, data=predplot, color=design, 
      group=interaction(subj_id, design), geom="line", alpha=I(0.1)) + 
  scale_color_manual("Plot Design", values=c("#33AA33", "#9977EE", "#FF9933", "#00DDAA")) + 
  xlab("Correlation") + ylab("Estimated Power") +
  geom_line(aes(y=FixedEf), size=2, alpha=1) + theme_bw() + facet_wrap(~t, ncol = 2) + theme(aspect.ratio=1.2)
@
  \caption{Predicted power fit from the mixed effects logit power model. The thicker lines shows the fixed effects prediction while the thinner lines show the range of random effects, the observer's visual ability. The weakness of the overlaid line graph in negative correlation and the scatter plot's gain from sample size are highlighted.}
  \label{powermodel}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='powermodel', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
randomeffects <- summarise(group_by(prediction, subj_id), re=max(diff))
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}

@@

The structure of the model ~\ref{timemodel} is similar to that in Equation~\ref{modelpower} except the link function is replace with the identity function, $\psi(x) = x$, and a new variable, $x_{6,m}$, is introduced with $m = \{0,1\}$ indicating if the subject detected the true plot, where $m = 0$ is a failure to detect the true plot.

\begin{table}[htp]
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines. Fitted with the MIXED procedure in SAS.}
\label{tab2}
\centering
<<timefit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
time.fit <- time.fit[c(1, 5, 6, 2, 3, 4, 7, 8, 12, 13, 9, 10, 11, 14),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "abs(r)", "sign(r)", "abs(r)*sign(r)", "detected", "design", "design*Smoothed", "design*t", "design*abs(r)", "design*sign(r)", "design*abs(r)*sign(r)", "design*detected")
time.fit$Effect <- NULL
colnames(time.fit) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(time.fit[1:14,], format="latex", digits=2)
@
\end{table}

@@

\begin{table}[htbp]
\caption{The true plot detections / attempts for each lineup in the data collection. Results ignore multiple selection weighting. True plot correlation is on the x axis and t is on the y axis. }
\label{tab3}
\centering
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
turk.tbl <- select(bylineup, design, smoothed, r, n, correct, evals)
turk.tbl$result <- paste(round(turk.tbl$correct, 0), turk.tbl$evals, sep="/")
turk.tbl <- turk.tbl[order(turk.tbl$r, turk.tbl$n),]
scatter.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Scatterplot")$result, ncol=8))
scatter.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Scatterplot")$result, ncol=8))
line.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Overlaid Lines")$result, ncol=8))
line.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Overlaid Lines")$result, ncol=8))
colnames(scatter.uns) <- c("", "-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(scatter.sm) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.uns) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.sm) <- c("","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
kable(scatter.uns, format="latex", caption="Unsmoothed scatter plot results")
kable(scatter.sm, format="latex", caption="Smoothed scatter plot results")
kable(line.uns, format="latex", caption="Unsmoothed overlaid line results")
kable(line.sm, format="latex", caption="Smoothed overlaid line results")
@
\end{table}

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in the United States but some are spread around other countries in Europe and Asia.}
\label{map}
\end{figure}
